---
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# Intro to Data Science - Lab 10
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 10 - Association	Rules	Mining

```{r}
# Enter your name here: Hongdi Li
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
```

**Association	rules	mining**,	also	known	as	**market	basket	analysis**,	is	an **unsupervised	data	mining	technique**	that	discovers	patterns	in	the	form	of	if-then	rules. The	technique	is	** unsupervised **	in	the	sense	that	there	is	no	prediction	or	classification	happening.	We	are	simply	trying	to	find	interesting **patterns**.	<br><br>
In	addition	to	working	with	 baskets 	of	objects,	association	rules	mining	is	good	at	working	with	any	kind	of	data	that	can	be	expressed	as	**lists	of	attributes**.	For	example,	a	trip	to	Washington	DC	might	consist	of	the	following	attributes:	train,	July,	morning	departure,	afternoon	arrival,	Union	Station,	first	class,	express.	<br><br>

In	these	exercises	we	will	work	with	a	built	in	data	set	called **groceries**.		Make	sure	
to library	the	**arules**	and	**arulesViz**	packages	before	running	the	following:	<br><br>


```
data (Groceries) # Load data into memory
myGroc <- Groceries # Make a copy for safety
```


```{r}
library(arules)
library(arulesViz)

data (Groceries) # Load data into memory
myGroc <- Groceries # Make a copy for safety
```

1. Examine the data structure that **summary()** reveals.	This	is	called	a	**sparse matrix** and it efficiently stores a set of market baskets along with meta-data. Report using R comments about some of the item labels.

```{r}
summary(myGroc)
```

2. Use	the	**itemFrequency(myGroc)**	command	to	generate	a	list	of	item
frequencies.	Save	that	list	in	a	new	data	object.	Run	**str( )**	on	the	data	object
and	write	a	comment	describing	what	it	is.	Run	**sort( )**	on	the	data	object	and
save	the	results.	Run	**head( )** and	**tail( )** on	the	sorted	object	to	show	the
most	and	least	frequently	occurring	items.	What s	the	most	frequently
purchased	item?

```{r}
list<-itemFrequency(myGroc)

str(list)
sort_list<-sort(list)

print('********************************************************')
head(sort_list)

print('--------------------------------------------------------')
tail(sort_list)

#the	most	frequently purchased	item is whole milk

```

3. Create	a	frequency	plot	with	`itemFrequencyPlot(myGroc, topN=20)`
and	confirm	that	the	plot	shows	the	most	frequently	purchased	item	with	the
left-most	bar.	Write	a	comment	describing	the	meaning	of	the	Y-axis.

```{r}
itemFrequencyPlot(myGroc, topN=20)
# y- bar shows the frequency of each item bought by people.
```

4. Create	a	cross	table	with	`ct	<-	crossTable(myGroc,	sort=TRUE)`.	Examine	the	first
few	rows	and	columns	of	**ct**	by	using	the	square	brackets	subsetting	technique.
For	example,	the	first	two	rows	and	first	three	columns	would	be	`ct[1:2,	1:3]`.
Write	a	comment	describing	one	of	values.	Write	a	comment	describing	what	is
on	the	diagonal	of	the	matrix.

```{r}
ct	<-	crossTable(myGroc,	sort=TRUE)
ct[1:2,	1:3]
```

5. Run	the	following	analysis:<br><br>


```
rules1 <- apriori(myGroc,
 parameter=list(supp=0.0008, conf=0.55),
 control=list(verbose=F),
 appearance=list(default="lhs",rhs=("bottled beer")))
```



```{r}
rules1 <- apriori(myGroc,
 parameter=list(supp=0.0008, conf=0.55),
 control=list(verbose=F),
 appearance=list(default="lhs",rhs=("bottled beer")))
```

6. Examine	the	resulting	rule	set	with	**inspect(	)**	and	make	sense	of	the	results.
There	should	be	four	rules	in	total.

```{r}
inspect(rules1)
```

7. Adjust	the	**support**	parameter	to	a	new	value	so	that	you	get	more	rules.
Anywhere	between	10	and	30	rules	would	be	fine.	Examine	the	new	rule	set
with	**inspect(	)**.	Does	your	interpretation	of	the	situation	still	make	sense?

```{r}
rules2 <- apriori(myGroc,
 parameter=list(supp=0.0005, conf=0.55),
 control=list(verbose=F),
 appearance=list(default="lhs",rhs=("bottled beer")))

```

```{r}
inspect(rules2)
```

8. Power	User (not required):	use	**mtcars**	to	create	a	new	data frame	with	**factors**	(e.g.,	cyl attribute).	Then	create	an	mpg	column	with	 good 	or	 bad 	(good	MPG	is above 25).	Convert	the	data frame	to	a	transactions	dataset	and	then	predict	rules	for having	bad	MPG.
```{r}
data(mtcars)
str(mtcars)
```

```{r}
df <- data.frame(cyl=as.factor(mtcars$cyl),
                       good_mpg=as.factor(na.omit(mtcars$mpg)>25),
                        bad_mpg=as.factor(na.omit(mtcars$mpg)<25))
```

