
# Intro to Data Science - Lab 1
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 1 - Introduction to R

```{r}
# Enter your name here: Hongdi Li
```

### Please include nice comments. <br>
### Instructions: 
In your group, introduce yourselves to each other and then solve each of the problems below: I may ask you the names of the people in your group!<br>
All students in the group should be prepared to report the whole class at the
conclusion of the breakout group. All students should run the necessary code on
their own instances of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
```

Each student should run R-Studio on their computer (or via https://rstudio.cloud/).
Remember that R should always be installed before R-Studio (if you are not using
rstudio.cloud or Google Colab)

1. Add together all the numbers between 1 and 10 (inclusive). Take note of the result. Remember, every student should type and run the code on their machine.

```{r}
1+2+3+4+5+6+7+8+9+10
#This is adds of first 10 numbers
```

2. Now	create	a	vector	of	data	that	contains	the	numbers	between	1	and	10
(inclusive).	Here	is	a	line	of	code	to	do	that: <br>

`myNumbers <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)`

```{r}
myNumbers<-c(1,2,3,4,5,6,7,8,9,10)
myNumbers #To show the output
#The output is 1 2 3 4 5 6 7 8 9 10

```

3. Now add together all of the numbers that are in the vector **myNumbers**. There is a built-in function within R that can do this for you in one step: Take a guess as to the name of that function and run it on **myNumbers**. Check your result against the results of question 1.

```{r}
sum(myNumbers)
#I use the sum() function and get the same answer which is 55
```

4. R can do a powerful operation called ** vector math ** in which a calculation runs on every element of a vector. Try vector math on **myNumbers** by adding 10 to each element of myNumbers, and storing the result in **myNewNumbers**. Print out **myNewNumbers**.

```{r}
myNewNumbers<-10+myNumbers
myNewNumbers #To show the out put 
```

5. Efficiently calculate a sum of the numbers between 11 and 20 (inclusive), using techniques from the problems above. **Hint:** use `c(11:20)`

```{r}
sum(11:20)
#use the sum() function to sum the numbers between 11 and 20
```

6. Calculate a sum of all of the numbers between 1 and 100 (inclusive), using techniques from the problems above.

```{r}
sum(1:100)
#use the sum() to get the sum of all of the numbers between 1 and 100
```


7. Make sure you have a variable **myNumbers**, that is a vector of 10 numbers (1,2,3,4,5,6,7,8,9,10)

```{r}
myNumbers
#To show what inside the vector----myNumbers
```

8. Type the following commands in the code cells below and run each one: 

<br>`mean(myNumbers)` <br>`median(myNumbers)` <br>`max(myNumbers)` <br>`min(myNumbers)` <br>`length(myNumbers)`

```{r}
mean(myNumbers)
# get the mean value from 1 to 10
```

```{r}
median(myNumbers)
# get the median value from 1 to 10
```

```{r}
max(myNumbers)
# get the max value from 1 to 10
```

```{r}
min(myNumbers)
# get the mean value from 1 to 10
```

```{r}
length(myNumbers)
# get the leagth of "myNumbers"
```

9. Repeat the commands from above, this time adding a comment to each line of code in your file explaining what it does. The comment character is  # .

```{r}
mean(myNumbers)
# get the mean value from 1 to 10
```

```{r}
median(myNumbers)
# get the median value from 1 to 10
```

```{r}
min(myNumbers)
# get the mean value from 1 to 10
```

```{r}
max(myNumbers)
# get the max value from 1 to 10
```

```{r}
length(myNumbers)
# get the leagth of vector "myNumbers"
```

10. In a comment, explain the output of the following command: <br> `myNumbers > 5`

```{r}
myNumbers > 5
# let every elemnts in vector myNumbers compare with the number 5 to see if it larger than 5, then return a bool value.
```

11. Explain what in is **bigNum** after executing the following command: 

`bigNum <- myNumbers[myNumbers > 5]`

```{r}
bigNum <- myNumbers[myNumbers > 5]
bigNum
#all the elements in vector bigNum is [6,7,8,9,10], which gives the number that larger than 5
```

12. Whenever you need R to explain what a command does and how it works, use the **?** command or the **help()** command. Add and run these commands: <br>
`?mean` <br>`help("mean")`

```{r}
help("mean")
# it gives me the def of "Mean" and it tell me how to use the mean() function

```

```{r}
?mean
# it gives me the def of "Mean" and it tell me how to use the mean() function
```

