---
output:
  word_document: default
  pdf_document: default
  html_document: default
---

# Intro to Data Science - Lab 2
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 2 - Sorting Data and Ordering a Data Frame

```{r}
# Enter your name here: Hongdi Li
```

### Please include nice comments. <br>
### Instructions: 
In your group, introduce yourselves to each other again and then solve each of the problems below: I may ask you the names of the people in your group!<br>
All students in the group should be prepared to report the whole class at the
conclusion of the breakout group. All students should run the necessary code on
their own instances of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.

```

1. Make	a	copy	of	the	built-in	iris	data	set	like	this:<br>
`myIris	<-	iris`

```{r}
myIris	<-	iris
```

2. Get	an	explanation	of	the	contents	of	the	data	set	with	the	**help()**	function:<br>
`help("iris")`

```{r}
help(iris)
```

3. Explore	**myIris**	via the	**str()**	and	**glimpse()**	functions	(note:	you	need	to	install	and
library	** tidyverse **	to	use	**glimpse()**).	Which	do	you	think	is	better?	Why? Explain in a comment.

```{r}
#install.packages('tidyverse')
library(tidyverse)
str(myIris)
glimpse(myIris)

#I think glimpse() is way mych better because it can format the data
#glimpse() let the data value in double type thus more accurate
```

4. Summarize	the	variables	in	your	copy	of	the	data	set,	like	this:<br>
`summary(myIris)`

```{r}
summary(myIris)
```

5. The	**summary()**	command	provided	the	mean	of	each	numeric	variable.	Choose
the	variable	with	the	highest	mean and	list	its	contents.	Any
variable	can	be	echoed	to	the	console	simply	by	typing	its	name.	Here s	an
example	that	echoes	the	variable	with	the	lowest	mean:<br>
`myIris$Petal.Width`

```{r}

high_mean<-myIris$Sepal.Length 
high_mean
```

6. Now	sort	that attribute by	calling	the	**sort()**	function	and	supplying	that	variable.
Remember	to	choose	the	variable	with	the	highest	mean.

```{r}
sort_high<-sort(high_mean)
sort_high
```

7. Now	repeat	the	previous	command,	but	this	time	use	the	**order()**	function,	again
using the	variable	with	the	highest	mean.

```{r}

order(high_mean)

```

8. Write	a	comment	in	your	R	code	explaining	the	difference	between	**sort()**	and
**order()**.	Be	prepared	to	explain	this	difference	to	the	class.

```{r}
#sort() basic shows the output data value as the increasing order,
#but order() shows the position of the each data value, it wont tell user what's the data set's value
# For example:
#input: e<- c(0.1 0.3 0.2)
#order(e) shows 1 3 2, which 1 means 0.1, 3 means 0.2 ... 
#sort(e) shows 0.1 0.2 0.3
```

9. Now	use	the	**order()**	command	to	reorder	the	whole	data	frame, and	store	the	new
dataframe	in	a	variable	called	** sortedDF **:

```{r}
sortedDF<-order(myIris)

```

10. Now	sort	the	dataframe	using	**arrange()**,	which	is	part	of	the	**tidyverse**	package.
This	time,	sort	based	the attribute	with	the	lowest mean.	Store	the	new
dataframe	in	a	variable	called	** sortedDF1 **

```{r}
sortedDF1<-arrange(myIris,Petal.Width)


```

11. Finally,	use	**head()**	to	examine	your	reordered	data	frames	and	be	prepared	to
report	on	the	first	few	rows


```{r}
head(sortedDF)
head(sortedDF1)
```

12. What	does	the	following	line	of	code	do?<br>
`myIris [	,	1]`

```{r}

myIris [	,	1]
#shows the first colunms
```

13. What	is	the	difference	(if	any)	between:<br>
`myIris [	,	"Sepal.Length"]` and <br> 
`myIris $Sepal.Length`

```{r}
myIris [	,	"Sepal.Length"]
myIris $Sepal.Length

#they are same
```

14. Write	the	R	code	that	outputs	the	** Sepal.Length **	attribute	values,	using	the **select()**	command.

```{r}
select(myIris,Sepal.Length)
```

15. Create	a	new	column	(called	** Ave.Length **)	in	**myIris**,	which,	for	each	row,	is	the average	of	**Sepal.Length**	and	**Petal.Length**.

```{r}
myIris$Ave.Length<-c((myIris$Sepal.Length+myIris$Petal.Length)/2)
myIris


```

16. What	does	the	following	line	of	code	do:<br>
`which.min(myIris$Petal.Length)`

```{r}

which.min(myIris$Petal.Length)
#tell the user which position in the data set is the min value.
```

17. Using	the	code	from	the	previous	step,	output	the	row	(iris	observation)	with	the
smallest	petal	length.

```{r}
min<-which.min(myIris$Petal.Length)
myIris$Petal.Length[min]
```

18. Create	a	new	dataframe,	with	just	the	**Petal.Length**	and	**Petal.Width** attributes

```{r}
new_frame<-data.frame(select(myIris,Petal.Length),select(myIris,Petal.Width))
new_frame
```

19. Create	a	new	dataframe,	using	the	**slice()**	function,	with	only	the	first	three	rows
in	the	**myIris**	dataframe.

```{r}
new_frame2<-slice(myIris,1:5)
new_frame2

```

20. Create a	new	dataframe,	which	is	a	subset	of	**myIris**,	that	only	includes	rows
where **Petal.Length is	less	than	1.4**,	store	in	**shortPetalDF**

```{r}
shortPetalDF<-subset(myIris,myIris$Petal.Length<1.4)
shortPetalDF
```

21. How	many	rows	are	in	the	**shortPetalDF**?

```{r}
length(shortPetalDF[,1])
```

22. The	homework	asks	you	to	create	a	conditional	statement	with	**if**	and	**else**.	A
conditional	statement	is	part	of	a	larger	group	of	specialized	commands	that
control	the	 flow 	of	a	program	 	what	command	gets	run	and	when.	You	can	get
help	on	if,	else,	and	other	control	words.	Add	and	run	these	commands:<br>
`help("if")` <br>
`help("Control")`<br>
Now	add	and	run	your	first	conditional	statement:<br>
`if	(sum(myNumbers)	>	40)	print("The	sum	is	greater	than	40.")`

```{r}
myNumbers<-c(20,30,40)
if	(sum(myNumbers)	>	40)	print("The sum is greater than 40.")
```

```{r}
myNumbers<-c(2,3,4)
if(sum(myNumbers)	>	40){
  	print("The sum is greater than 40.")}else
  	print("The sum is less than 40")
```

```{r}

ans<-0
for(i in 1:10){
 
    ans<-ans+i
    
}
ans

```


```{r}
b<-100
if(b>50){
  print("test")
}else
  print("fail")
```

```{r}
names <- c("Alex","Shu", "Tanya")

ages <- c(28,17,35)

users <- c("alp@syr.edu","sh67@syr.edu","tans@syr.edu")

students <- data.frame(names,ages,users)
students[2,3]


```