---
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# Intro to Data Science - Lab 6
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 6 - Using	ggplot	to	Build	 Complex	Data	Displays

```{r}
# Enter your name here: Hongdi Li
```

```{r}
#install.packages('imputeTS')
#libary(imputeTS)
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.

```

Creating	graphical	displays	of	data	is	an	essential	skill	for	all	data	scientists	because	so	much	of	what	data	scientists	do	involves	communicating	with	other	people	about	data.	The	**ggplot2**	package	developed	by	data	scientist	Hadley	Wickham (https://en.wikipedia.org/wiki/Hadley_Wickham)	provides	excellent	power	and	flexibility	for	graphically	displaying	data.	Whole	books	have	been	written	about	**ggplot2**	(e.g.:	https://www.springer.com/gp/book/9780387981413 ),	so	we	will	only	be	able	to	scratch	the	surface,	but	we	will	master	the	basic	 grammar 	that	you	need	in	order	to	use	this	
package.	<br><br>For	this lab we	will	also	use	a	dataset	that	comes	delivered in R,	called	** economics **. It contains	574	 snapshots	of	U.S.	economic	conditions	between	1967	and	2014.<br><br>		
Here	are	two lines	of	starter	code:	<br><br>


```
MyPlot <- ggplot(economics, aes(x=date),inherit.aes = FALSE)
myPlot <- MyPlot + geom_line(aes(y=psavert))
```


1. Run	these	two lines	of	code below.	What	happens?	How	do	you	actually	 invoke 	the plot	
(i.e.,	how	do	you	get	it	to	draw	in	the	plot	window)?

```{r}
library(ggplot2)
MyPlot <- ggplot(economics, aes(x=date),inherit.aes = FALSE)
myPlot <- MyPlot + geom_line(aes(y=psavert))
#will create a graph and saved in myPlot.
#First, step get the x-axis with the date, and saved in MyPlot
#Then, add y-axis and draw the graph based on Myplo
#Get the new graph and saved in myPlot 
```

2. Run `help("economics")` to	find	out	the	meaning	of	the	**psavert**	variable.

```{r}
help("economics")
# which means the personal saving sate
```

3. Examine	the	plot	to	estimate	when	the	personal	savings	rate	reached	its maximum	
value.	Also	examine	the	plot	to	estimate	when	the	personal	savings rate	reached	its	
minimum	value.

```{r}
myPlot
#around 1975 reach the maximum, 2005 reach the minimum
```

4. Use	**which.max(	)**	and	**which.min(	)**	to	verify	your	guesses	from	problem	3.

```{r}
economics$date[which.max(economics$psavert)]
economics$date[which.min(economics$psavert)]
#Almost same the 1975-05-01 reach max
# 2005-07-01 reach the minimum
```

5. Change	the	color	of	the	plot	line	to	green.<br><br>	**Hint:** Changing	a	line	to	a	constant color	happens	in	the	specification	of	the	**geometry**.

```{r}
myPlot <- MyPlot + geom_line(aes(y=psavert),color='green')
myPlot
```

6. Add	a	title	to	the	plot	with	the	**ggtitle("Put	title	here")**	sub-command.	The	title **"Personal	Savings	Rate:	1967-2014"** would	be	a	good	choice.

```{r}
myPlot <- MyPlot + geom_line(aes(y=psavert),color='green')+ggtitle("Personal Savings Rate:	1967-2014")
myPlot
```

7. Add	another	data	series	to	your	plot	to	show	the	variable	**uempmed**	as	a	red line.

```{r}
new_plot <- myPlot + geom_line(aes(y=uempmed),color="red")
new_plot
```

8. Change	the	title	of	the	plot	to	mention	both	variables.

```{r}
myPlot <- MyPlot + geom_line(aes(y=psavert),color='green')+ggtitle("Personal Savings and Median Weeks Unemployed Rate:	1967-2014")
new_plot <- myPlot + geom_line(aes(y=uempmed),color="red")
new_plot
```

9. You	can	modify	the	axis	labels	in	a	ggplot	with	**ylab(	)**	and	**xlab(	)**	subcommands.
Change	the	axis	labeling	as	needed	to	account	for	plotting	both **psavert**	and **uempmed**	 in	the	same	window.

```{r}
New<-new_plot+ylab("uempmed & psavert")
New
```

10. Create	one	last	plot,	creating	a	scatter	plot,	having	the	**unemploy** on	the	x-axis, **psavert**	
on	the	yaxis.	Color	each	point	based	on	the	**uempmed**.

```{r}
ggplot(data=economics,aes(x=unemploy,y=psavert,color=uempmed))+geom_point()
```

11. Interpret	(using comments in R) what	you	see	in	this	last	graph.

```{r}
#I can see a scatter plot with the relation between
#unemploy and psavert and they colored based on the uempmed variable
```

