---
output:
  pdf_document: default
  html_document: default
---

# Intro to Data Science - Lab 7
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 7 - Using	ggplot	to	Build	 Complex	Data	Displays

```{r}
# Enter your name here: Hongdi Li
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
```

 Geology rocks but geography is where it's at. . .  (famous dad joke). In
a global economy, geography has an important influence on everything from
manufacturing to marketing to transportation. As a result, most data scientists will
have to work with map data at some point in their careers. <br><br>

An add-on to the **ggplot2** package, called **ggmap**, provides powerful tools for plotting and shading maps.<br><Br>
Make sure to install the **maps**, **mapproj**, and **ggmap** packages before running the following:



```
library(ggplot2); library(maps); library(ggmap); library(mapproj)
us <- map_data("state")
us$state_name <- tolower(us$region)
map <- ggplot(us, aes(map_id= state_name))
map <- map + aes(x=long, y=lat, group=group) +
geom_polygon(fill = "white", color = "black")
map <- map + expand_limits(x=us$long, y=us$lat)
map <- map + coord_map() + ggtitle("USA Map")
map
```



1. Paste the code below and add a comment for each line, explaining what that line of code does.

```{r}
library(ggplot2); library(maps); library(ggmap); library(mapproj)
#library the package we going to use

us <- map_data("state")
# transform data to dataframe

us$state_name <- tolower(us$region)
# create a new column which store the lower letter of the data in us => region.

map <- ggplot(us, aes(map_id= state_name))
map <- map + aes(x=long, y=lat, group=group) +
geom_polygon(fill = "white", color = "black")
# use ggplot draw polygons function to create the US map 

map <- map + expand_limits(x=us$long, y=us$lat)
#Extend the drawing bounds of the graph base on the long and lat data.

map <- map + coord_map() + ggtitle("USA Map")
#Spherical map projected on a plane and add the title

map
```

2. The map you just created fills in the area of each state in white while outlining it with a thin black line. 
First step: Use the **fill=** and **color=** commands inside the call to **geom_polygon( )** to reverse the color scheme.<br><br> using the code from #1.

Second step: Now paste and run the following code:<br><br>


```
ny_counties <- map_data("county","new york")
ggplot(ny_counties) + aes(long,lat, group=group) + geom_polygon(fill
= "white", color = "black")
```


```{r}
# From #1

map <- ggplot(us, aes(map_id= state_name))
map <- map + aes(x=long, y=lat, group=group) +
geom_polygon(fill = "black", color = "white")
# use ggplot draw polygons function to create the US map 

map <- map + expand_limits(x=us$long, y=us$lat)
#Extend the drawing bounds of the graph base on the long and lat data.

map <- map + coord_map() + ggtitle("USA Map")
#Spherical map projected on a plane and add the title
map

ny_counties <- map_data("county","new york")
ggplot(ny_counties) + aes(long,lat, group=group) + geom_polygon(fill
= "white", color = "black")
```

3. Just as in step 2, the map you just created fills in the area of each county in black
while outlining it with a thin white lines. Use the **fill=** and **color=** commands
inside the call to **geom_polygon( )** to reverse the color scheme.

```{r}
ggplot(ny_counties) + aes(long,lat, group=group) + geom_polygon(fill
= "black", color = "white")
```

4. Run `head(ny_counties)` to verify how the county outline data looks

```{r}
head(ny_counties)
```

5. Make a copy of your code from step 3 and add the following subcommand to
your ggplot( ) call (don t forget to put a plus sign after the **geom_polygon( )** statement to tell R that you are continuing to build the command):<br><br>
`coord_map(projection = "mercator")` <br><br>
In what way is the map different from the previous map. Be prepared to explain
what a Mercator projection is. 

```{r}
ggplot(ny_counties) + aes(long,lat, group=group) + geom_polygon(fill
= "black", color = "white")+coord_map(projection = "mercator")
#The new image map is zoomed and narrower in width than the original map
                                      
```

6. Grab a copy of the nyData.csv data set from:
https://intro-datascience.s3.us-east-2.amazonaws.com/nyData.csv
<br><br>Read that data set into R with **read_csv()**. This will require you have installed
and libraried the **tidyverse** package. The next step assumes that you have named the
resulting data frame ** nyData. **

```{r}
library(tidyverse)
nyData<-read.csv('https://intro-datascience.s3.us-east-2.amazonaws.com/nyData.csv')
```

7. Next, merge your **ny_counties** data from the first set of
questions with your new **nyData** data frame, with this code:<br><br>
`mergeNY <- merge(ny_counties,nyData,all.x=TRUE,by.x="subregion",by.y="county")`



```{r}
mergeNY <- merge(ny_counties,nyData,all.x=TRUE,by.x="subregion",by.y="county")
```

8. Run `head(mergeNY)` to verify how the merged data looks.

```{r}
head(mergeNY)
```

9. Now drive the fill color inside each county by adding the **fill** aesthetic inside of
your **geom_polygon( )** subcommand (fill based on **pop2000**).

```{r}
ggplot(mergeNY) + aes(long,lat, group=group) + geom_polygon(aes(fill
= pop2000), color = "white")+
  coord_map(projection = "mercator")
```

10. Extra (not required):<br>
a. Read in the following JSON datasets:
'https://gbfs.citibikenyc.com/gbfs/en/station_information.json'
'https://gbfs.citibikenyc.com/gbfs/en/station_status.json'<br>
b. Merge the datasets, based on ** station_id **<br>
c. Clean the merged dataset to only include useful information<br>
For this work, you only need lat, lon and the number of bikes available
d. Create a stamen map using ** get_stamenmap() **<br>
Have the limits of the map be defined by the lat and lot of the stations<br>
e. Show the stations, as points on the map.<br>
f. Show the number of bikes available as a color

```{r}
library(RCurl)
library(jsonlite)

##part: a
url_1<-'https://gbfs.citibikenyc.com/gbfs/en/station_information.json'
url_2<-'https://gbfs.citibikenyc.com/gbfs/en/station_status.json'

api_1<-getURL(url_1)
api_2<-getURL(url_2)

data1<-fromJSON(api_1)
data2<-fromJSON(api_2)


##part: b
data<-merge(data1,data2)


##part: c
df<-subset(data,select=c(data.stations.lat,data.stations.lon,data.stations.num_bikes_available))

head(df)


##part: d
bbox <- c(bottom = min(df$data.stations.lat), top = max(df$data.stations.lat) , right = max(df$data.stations.lon), left = min(df$data.stations.lon))

mp <- get_stamenmap( bbox) 

##part: e
p <- ggmap(mp)+geom_point(data = df, mapping = aes(x =data.stations.lon, y = data.stations.lat))


##part: f
p <- ggmap(mp)+geom_point(data = df, mapping = aes(x =data.stations.lon, y = data.stations.lat,color = data.stations.num_bikes_available))
  


p
#show p

```

