---
output:
  pdf_document: default
  html_document: default
---

# Intro to Data Science - Lab 8
##### Copyright 2022, Jeffrey Stanton and Jeffrey Saltz   Please do not post online.

## Week 8 - Linear Models

```{r}
# Enter your name here: Hongdi Li
```

### Please include nice comments. <br>
### Instructions: 
Run the necessary code on your own instance of R-Studio.

### Attribution statement: (choose only one and delete the rest)

```{r}
# 1. I did this lab assignment by myself, with help from the book and the professor.
```

**Linear	modeling**,	also	referred	to	as	**regression	analysis**	or	multiple regression **bold text**,	is	a	technique	for	fitting	a	line,	plane,	or	higher	order	linear	object	to	data.	<br><br>In	their	simplest	form,	linear	models	have	one	metric	**outcome	variable**	and	
one	or	more	**predictor	variables**	(any	combination	of	metric	values,	ordered	
scales	such	as	ratings,	or	dummy	codes).			<br><br>

Make	sure	to	library	the	**MASS**	and	**ggplot2** packages	before	running	the	following:	<br><br>


```
ggplot(data=Boston) + aes(x=rm, y=medv) + geom_point() +
 geom_smooth(method="lm", se=FALSE)
```



```{r}
library(MASS)
library(ggplot2)
ggplot(data=Boston) + aes(x=rm, y=medv) + geom_point() + geom_smooth(method="lm", se=FALSE)
```

1. Explore	this	dataset	descrption	by	typing	`?Boston` in a code cell.

```{r}
?Boston
```

2. The graphic you just created fits a best line to a cloud of points. Copy and
modify the code to produce a plot where ** crim ** is the x variable instead of ** rm**. 

```{r}
ggplot(data=Boston) + aes(x=crim, y=medv) + geom_point() + geom_smooth(method="lm", se=FALSE)
```

3. Produce a histogram and descriptive statistics for **Boston$crim**. Write a
comment describing any anomalies or oddities.

```{r}
hist(Boston$crim)
#The freq is really high at 0 and reduce fast
```

4. Produce a linear model, using the **lm( )** function where **crim** predicts **medv**.<br><br>
Remember that in R s formula language, the **outcome variable** comes first and is
separated from the predictors by a **tilde**, like this: `medv ~ crim`<br><br>
Try to get in the habit of storing the output object that is produced by lm and
other analysis procedures. For example, I often use **lmOut <- lm( . . .)**

```{r}
ans<-lm(Boston$medv~Boston$crim)
```

5. Run a **multiple regression** where you use **rm**, **crim**, and **dis** (distance to Boston employment centers). You will use all three predictors in one model with this
formula:<br><br> `medv ~ crim + rm + dis` <br><br>Now run three separate models for each
independent variable separate.

```{r}
a<-lm(medv ~ crim +dis + rm,data=Boston)
summary(a)
```

```{r}
b<-lm(Boston$crim ~ Boston$medv + Boston$rm + Boston$dis)
summary(b)
```

```{r}
c<-lm(Boston$rm ~ Boston$medv + Boston$crim + Boston$dis)
summary(c)
```

```{r}
d<-lm(Boston$dis ~ Boston$medv + Boston$rm + Boston$crim)
summary(d)
```

6. Interpret	the	results	of	your	analysis	in	a	comment.	Make	sure	to	mention	the	**p-value**,	the	**adjusted	R-squared**,	the	list	of **significant	predictors**	and	the	**coefficient** for	each	significant	predictor.

```{r}
#p vlaue for Boston$medv is <<0.05, but for others are larger than 0.05 thus,
#When controlling for other predictors unchanged, the linear relationship between rm and crim is not significant
#Multiple R-squared:  0.1611 and Adjusted R-squared:  0.1561 , So the predictors explain around 15-16% of the variance of dis
#It shows that when the above predictors are used to estimate dis, the average estimation error is 1.934
```

7. Create	a	one-row	**data	frame**	that	contains	some	plausible	values	for	the predictors.	For	example,	this	data	frame	contains	the	median	values	for	each predictor:<br><br> `predDF <- data.frame(crim = 0.26, dis=3.2, rm=6.2)`<br><br>
The numbers used here were selected randomly by looking at min and max data
of the variables.

```{r}
predDF <- data.frame(crim = 0.26, dis=3.2, rm=6.2)
```

8. Use	the	**predict( )** command	to	predict	a	new	value	of	**medv** from	the	one-row	data	frame.	If	you	stored	the	output	of	your	lm	model	in **lmOut**,	the command	would	look	like	this:<br><br>	`predict(lmOut, predDF)`

```{r}
predict(a, predDF)
```

